---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


```{r global_options, include=FALSE}
library(knitr)
library(ggplot2)
library(dmm)
opts_chunk$set(echo=TRUE,fig.width=12, fig.height=8)
```


## Loading and preprocessing the data
```{r}
activity <- read.csv('./activity/activity.csv')
```


## What is mean total number of steps taken per day?
```{r}
# Calculate total number of steps per day
total_steps <- tapply(activity$steps,activity$date,sum)
# Plot the histrogram
qplot(total_steps, geom="histogram")
# Calculate and report the mean and median 
mean.steps <- mean(total_steps, na.rm = TRUE)
median.steps <- median(total_steps, na.rm = TRUE)
```
The mean of total number of steps taken per day is `r mean.steps`. The meadian of total number of steps taken per day is `r median.steps`

## What is the average daily activity pattern?
```{r}
# Time Series plot of 5-mins daily avarage steps
fivemin.avg <- tapply(activity$steps, activity$interval, mean, na.rm=TRUE)
plot(unique(activity$interval),fivemin.avg,type='l',xlab='5-min interval', ylab='Daily Average')
#Get the maximum 5 mins interval
```
On Average across all days in the dataset, the `r names(which(fivemin.avg==max(fivemin.avg)))` 5-min interval contains the maximum number of steps.

## Imputing missing values
```{r}
# Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
na.total <- sum(is.na(activity$steps))
# Impute the missing values using the mean of that 5-min interval
#Create a new dataset that is equal to the original dataset but with the missing data filled in.
activity.new <- activity
activity.new$steps[is.na(activity$steps)]<- fivemin.avg[as.character(activity$interval[na.index])]

# Make a histogram of the total number of steps taken each day
# Calculate total number of steps per day
total_steps.new <- tapply(activity.new$steps,activity.new$date,sum)
# Plot the histrogram
qplot(total_steps.new, geom="histogram")
# Calculate and report the mean and median 
mean.steps.new <- mean(total_steps.new)
median.steps.new <- median(total_steps.new)
```

The total number of missing values in the dataset is `r na.total`.

The mean of total number of steps taken per day after imputing missing data is `r mean.steps.new`. The meadian of total number of steps taken per day after imputing missing data is `r median.steps.new`After observing from the previous data without imputing missing data, the mean does not change, the median changed a little bit. 


## Are there differences in activity patterns between weekdays and weekends?

```{r}
#Create a new factor variable in the dataset with two levels - "weekday" and "weekend" 
activity.new$date <- as.Date(activity.new$date, format = "%Y-%m-%d")

#create a vector of weekdays
weekdays1 <- c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday')
#Use `%in%` and `weekdays` to create a logical vector
#convert to `factor` and specify the `levels/labels`
activity.new$wDay <- factor((weekdays(activity.new$date) %in% weekdays1), levels=c(FALSE, TRUE), labels=c('weekend', 'weekday')) 

#panel plot for weekday and weekend data
par(mfrow=c(2,1))
activity.new.wkend <- activity.new[activity.new$wDay=="weekend",]
fivemin.avg.wkend <- tapply(activity.new.wkend$steps, activity.new.wkend$interval, mean)
plot(unique(activity.new.wkend$interval),fivemin.avg.wkend,type='l',xlab='5-min interval', ylab='Daily Average',main="weekend")

activity.new.wkday <- activity.new[activity.new$wDay=="weekday",]
fivemin.avg.wkday <- tapply(activity.new.wkday$steps, activity.new.wkday$interval, mean)
plot(unique(activity.new.wkday$interval),fivemin.avg.wkday,type='l',xlab='5-min interval', ylab='Daily Average',main="weekday")

```