---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


```{r global_options, include=FALSE}
library(knitr)
library(ggplot2)
opts_chunk$set(echo=TRUE,fig.width=12, fig.height=8)
```


## Loading and preprocessing the data
```{r}
activity <- read.csv('./activity/activity.csv')
```


## What is mean total number of steps taken per day?
```{r}
# Calculate total number of steps per day
total_steps <- tapply(activity$steps,activity$date,sum)
# Plot the histrogram
qplot(total_steps, geom="histogram")
# Calculate and report the mean and median 
mean.steps <- mean(total_steps, na.rm = TRUE)
median.steps <- median(total_steps, na.rm = TRUE)
```
The mean of total number of steps taken per day is `r mean.steps`. The meadian of total number of steps taken per day is `r median.steps`

## What is the average daily activity pattern?
```{r}
# Time Series plot of 5-mins daily avarage steps
fivemin.avg <- tapply(activity$steps, activity$interval, mean, na.rm=TRUE)
plot(unique(activity$interval),fivemin.avg,type='l',xlab='5-min interval', ylab='Daily Average')
#Get the maximum 5 mins interval
```
On Average across all days in the dataset, the `r names(which(fivemin.avg==max(fivemin.avg)))` 5-min interval contains the maximum number of steps.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
